### 2018-12-09 Sections/models_for_quantum_computation.tex
adiabatic minor comments for CV

\comment{To do}

>>>>

Adiabatic quantum computation (AQC) started as an approach to solving optimization problems, and has evolved into a universal alternative to the circuit model of quantum computing. 
AQC is based on an idea that is distinct from the circuit model \cite{RevModPhys.90.015002}. In the circuit model, the computation is encoded into a series of unitary quantum logic gates, whereas in AQC the computation starts from an initial whose ground state is easy to prepare, and evolves to a final state that encodes  the solution to the computation problem.

In the circuit model, the cost of the computation is equated with the number of gates. In AQC, Ahranov et al \cite{} defined the cost of adiabatic algorithm to be the dimensionless quantity

\begin{align}
\text{cost} = t_f \text{max}_s ||H(s)||
\end{align}
\noindent where $t_f$ is the run time, and $||\cdot||$ denotes the operator norm, which is the largest singular value of the operator.

The run time $t_f$ of an adiabatic algorithm scales at worst as $1/\Delta^3$, 
where $\Delta^3$ is the minimum eigenvalue gap between the ground state and the first excited state of the Hamiltonian\cite{}. This is the reason why AQC has generated much interest: it has a rich connection to well-studied condense matter physics.

The analysis for AQC involve bounding the eigenvalue gap of a complicated many-body Hamiltonian, which is a notoriously difficult problem. Nevertheless, a number of examples are known where a gap between classical and quantum. For example, adiabatic QC can perform a process analogous to Grover's search algorithm, providing a quadratic speed up over the best classical algorithm. Here we look at a few explicit algorithms for which AQC is known to give a speed up.
